Assessing primitives performance\\ on multi-stage execution

### 2018-05-09 paper.tex
added comments

@@

\begin{figure*}

@@

   \subcaption{Size 1000}
   \end{subfigure}
   \subcaption*{\textbf{LLVM-Mac results}\vspace{-0.5cm}}
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures}
   \label{fig:bench}
\end{figure*}

%\cba{Je pense string de taille 0-1 c'est cool pour montrer que le code C va moins vite que pur smalltalk dans ce cas (si c'est vraiment le cas)}
We performed the benchmarks upon 4 different string sizes: 0, 5, 100 and 1000 characters, using 2 different compilers: GCC on one hand and LLVM on the other hand. Figure \ref{fig:bench} show the results in terms of relative speed-up towards the baseline implementation\footnote{i.e. the pure Smalltalk version}, respectively for GCC and LLVM.

>>>>

\cba{Methodology section is missing here: each bench was run x times, each time being y comparison. We removed the loop overhead in the measurements. }
\cba{+ we bench only = strings, which could make a difference on the plugin version (one less branch) - maybe we should change to number of character compared instead of string size so it does not imply the string are equals.}
\cba{We are also missing exact results, aside from the graphs I usually expect a table with exact results and error margins... That's why the plot is often generated from a file, the table can reuse the same file and you can re-do your bench without changing the latex code. Cf https://hal.inria.fr/hal-01596321/document page 9, it would be nice here to have a similar table below the benchs}

@@

\begin{figure*}[bht]

@@

   \subcaption{Size 1000}
   \end{subfigure}
   \subcaption*{\textbf{LLVM-Mac results}\vspace{-0.2cm}} %change vspace based on fig position
    \end{subfigure}
   \caption{String comparison benchmarks for strings of different sizes on different architectures}
   \label{fig:bench}
\end{figure*}

%\cba{Je pense string de taille 0-1 c'est cool pour montrer que le code C va moins vite que pur smalltalk dans ce cas (si c'est vraiment le cas)}
We performed the benchmarks upon five different string sizes: 0, 1, 5, 100 and 1000 characters, using two different compilers: GCC on one hand and LLVM on the other hand. Figure \ref{fig:bench} show the results in terms of relative speed-up towards the baseline implementation\footnote{i.e. the pure Smalltalk version}, respectively for GCC and LLVM.
